Dark matter halo shapes at $z=0$ in the Auriga simulations

### 2019-07-21 Document/paper.tex
push

\begin{figure*}
\begin{center}
\subfloat[DMO simulations.]{\includegraphics[width=0.8\columnwidth]{Lvl_4_Triax_Plane_DM.pdf}}
\subfloat[MHD simulations.]{\includegraphics[width=0.8\columnwidth]{Lvl_4_Triax_Plane_MHD.pdf}}
\end{center}
\caption{Axial ratios for all halos in the simulation.
  Left/right panels correspond to DMO/MHD simulations, respectively.
  Triangles (squares) represent the measurements at $R_{200}/16$
  ($R_{200}$) which correspond to physical distances of $14\pm 1$ kpc
  ($230\pm 15$ kpc) respectively.
  Here we can visualize three main trends for the whole halo population.
  First, in DMO simulations halos are rounder in the outskirts
  than in the inner part.
  Second, halos in MHD are rounder than its DMO counterparts.
  Third, halos in MHD are less triaxial in the inner regions than in
  the outskirts.}
  \label{fig:triaxiality_plane}
\end{figure*}

\begin{figure*}
\subfloat[DMO simulations.]{\includegraphics[width=0.8\columnwidth]{triaxialiy_distro_DM.pdf}}
\subfloat[MHD simulations.]{\includegraphics[width=0.8\columnwidth]{triaxialiy_distro_MHD.pdf}}
\caption{Cumulative distribution for the triaxiality at five different radii.
  Right/left panel correspond to DMO/MHD simulations, respectively. 
  In DMO simulations the median triaxiality at all radii is larger
  than $0.5$; only for $20\%$ the triaxility is smaller than $0.5$.
  Furthermore, the triaxility increases as one moves towards the inner
  part of the halo.
  In MHD simulations the situation is reversed.
  The median triaxility at all radii is smaller than $0.5$.
  Moving towards the stellar disc the triaxility decreases towards a median
  value of $T=0.15$.}
\label{fig:triaxial_cumulative}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
\subfloat[DMO simulations.]{\includegraphics[width=0.8\columnwidth]{Lvl_4_Triax_Plane_DM.pdf}}
\subfloat[MHD simulations.]{\includegraphics[width=0.8\columnwidth]{Lvl_4_Triax_Plane_MHD.pdf}}
\end{center}
\caption{Axial ratios for all simulated halos.
  Left/right panel corresponds to DMO/MHD simulations, respectively.
  Triangles (squares) represent the measurements at $R_{200}/16$
  ($R_{200}$) that correspond to physical distances of $14\pm 1$ kpc
  ($230\pm 15$ kpc).
  Here we visualize three main population trends.
  First, in DMO simulations halos are rounder in the outskirts
  than in the inner part.
  Second, halos in MHD are rounder than its DMO counterparts.
  Third, halos in MHD are rounder in the inner regions than in
  the outskirts (opposite to the DMO trend).}
  \label{fig:triaxiality_plane}
\end{figure*}

\begin{figure*}
\subfloat[DMO simulations.]{\includegraphics[width=0.8\columnwidth]{triaxialiy_distro_DM.pdf}}
\subfloat[MHD simulations.]{\includegraphics[width=0.8\columnwidth]{triaxialiy_distro_MHD.pdf}}
\caption{Triaxility Cumulative distribution at five different radii.
  Right/left panel corresponds to DMO/MHD simulations, respectively. 
  In DMO simulations the median triaxiality at all radii is larger
  than $2/3$. Furthermore, the triaxility increases as one moves
  towards the inner part of the halo.
  In MHD simulations these trend reverses.
  The median triaxility at all radii is smaller than $1/3$ and the
  halo is less triaxial as on moves towards the stellar disc.}
\label{fig:triaxial_cumulative}
\end{figure*}
